Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-14 doc/camera-ready/paper.tex
Fix typo

\medskip
\begin{example}
  The abstract action set $A_F = \{\bar{a}, \bar{a}'\}$ where $\bar{a} = \abst{\neg H,n(x)>0}{H,n(x)\mminus}$
  and $\bar{a}'=\abst{H}{\neg H}$, defined over the above feature set $F=\{H,n(x)\}$,
  is sound but not complete relative to $\Q_{clear}$.
  The actions in $A_F$ captures the concrete actions that pick blocks from above $x$ and put them away,
  but not other actions like stacking a block above $x$, or picking a block that is not above $x$.
\end{example}

>>>>

\medskip
\begin{example}
  The abstract action set $A_F = \{\bar{a}, \bar{a}'\}$ where $\bar{a} = \abst{\neg H,n(x)>0}{H,n(x)\mminus}$
  and $\bar{a}'=\abst{H}{\neg H}$, defined over the above feature set $F=\{H,n(x)\}$,
  is sound but not complete relative to $\Q_{clear}$.
  The actions in $A_F$ capture the concrete actions that pick blocks from above $x$ and put them away,
  but not other actions like stacking a block above $x$, or picking a block that is not above $x$.
\end{example}
